Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2021-10-06 psy_peds_3.Rmd
fixing bug

```{r}
time_series_analysis_plotting(ts_seasonal_count,
                              patient_count_psy_period_psy, "count_psy",
                              clearance_period = FALSE) +
  labs(title = "Interrupted Time-Series Analysis: Percentage of encounters with psychiatric ICD codes",
       subtitle = "With seasonality effect",
       x = time_period,
       y = "Count")
```

@@

```{r}
time_series_analysis_plotting(ts_seasonal_count_clear,
                              patient_count_psy_period_psy, "count_psy",
                              clearance_period = TRUE) +
  labs(title = "Interrupted Time-Series Analysis: Count of encounters with psychiatric ICD codes",
       subtitle = "With seasonality effect",
       x = time_period,
       y = "Count")
```

>>>>

```{r}
time_series_analysis_plotting(ts_seasonal_count,
                              patient_count_psy_period_psy,
                              "count_psy_patients",
                              clearance_period = FALSE) +
  labs(title = "Interrupted Time-Series Analysis: Percentage of encounters with psychiatric ICD codes",
       subtitle = "With seasonality effect",
       x = time_period,
       y = "Count")
```

@@

```{r}
time_series_analysis_plotting(ts_seasonal_count_clear,
                              patient_count_psy_period_psy,
                              "count_psy_patients",
                              clearance_period = TRUE) +
  labs(title = "Interrupted Time-Series Analysis: Count of encounters with psychiatric ICD codes",
       subtitle = "With seasonality effect",
       x = time_period,
       y = "Count")
```
